\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Nishant Garg} \\ \vspace{1pt}
    \small \href{tel:12499990499}{\underline{+1(249)9990499}} $|$
    \href{mailto:gargn4@mcmaster.ca}{\underline{gargn4@mcmaster.ca}} $|$ 
    \href{https://www.linkedin.com/in/gargn4}{\underline{linkedin.com/in/gargn4}} $|$
    \href{https://github.com/nishx09}{\underline{github.com/nishx09}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{McMaster University} $|$ \small Honours Computer Science (Co-op) (Bachelor of Applied Science) }{\textit{\small Sep. 2019 -- May 2024}}
      {}{}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA: 4.0/4.0} $|$ Provost's Honour Roll $|$ Dean's Honour List $|$ recieved Edwin Marwin Dalley Mem Scholarship}
        \resumeItem{Relevant courses: data structure, algorithms, discrete mathematics, software development, web development}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small \item \textbf{Languages}{: \small  C, C++, Java, Python, Bash, HTML, CSS, SQL, JQuery, JavaScript, Haskell} \\
    \vspace{0.0001cm}
    \small \item \textbf{Frameworks}{: Django, Bootstrap} \\
    \vspace{0.0001cm}
    \small \item \textbf{Developer Tools}{: Git, Github, Gitlab, VS Code, Atom, PyCharm, IntelliJ, Eclipse, Unix Shell, Vim, \LaTeX} \\
    
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{McMaster University} $|$ \small Undergraduate Teaching Assistant \textbf{(CS1MD3)}}{\textit{\small Sep. 2020 -- Dec. 2020}}
      \resumeItemListStart
        \resumeItem{Supported instructor with test administration, curriculum development and assignment grading.}
        \resumeItem{Supported student learning objectives through personalized and small group assistance.}
        \resumeItem{Eliminated learning gaps and effectively instructed students on their programming skills using wide variety of teaching aids and motivational strategies.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NewsDistributor} $|$ \small{Java, PHP, MySQL}}{\small \textit{Sep 2018 -- Nov. 2018}}
          \resumeItemListStart
            \resumeItem{Developed an user interactive web application using java, php and mySQL}
            \resumeItem{Which allows the newspaper distributor to maintain the record of their customers and calculate the money due from different customers based on the newspaper they get.}
            \resumeItem{It also automatically sends the customers a mail regarding the amount due from the distributor.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BloodLine} $|$ \small{HTML, CSS, Bootstrap, Javascript, MySQL}}{\small \textit{Dec. 2018 -- Feb. 2019}}
          \resumeItemListStart
            \resumeItem{Developed an user interactive web page using HTML, CSS, Javascript and mySQL.}
            \resumeItem{Which allows the donors to locate the blood banks near them which is in need of their blood group and other way around if a person is in need of a particular blood group, it helps them to locate the blood bank with the required group.}
            \resumeItem{It also allows the user to contact their source through the very same web page.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ponder} $|$ \small{React Native, Javascript, SQLite, Git}}{\small \textit{Hack Western VII $|$ Nov. 2020}}
          \resumeItemListStart
            \resumeItem{Ponder is an app which allows the user to write journal entries about whatever they're grateful for.}
            \resumeItem{We built the frontend using React Native, using Expo CLI and backend using SQLite.}
            \resumeItem{We built this app to inspire the user be optimistic in the most stressful times and to help keep them on track and focused.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%------------EXTRA-CURRICULAR-------------
\section{Extra Curricular}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{McMaster Intramural League}}{\small \textit{Jan. 2020 -- March 2020}}
      \resumeItemListStart
        \resumeItem{Participated in the cricket intramural.}
      \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Developer Student Club McMaster University}}{\small \textit{Sep. 2020 -- Present}}
      \resumeItemListStart
        \resumeItem{Volunteered as a team member of the DSC external relations club.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
